Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

There are two stages that will be carried out to do this experiment, the first is baseline data collection stage. Baseline data will be taken by simulating
the usage of the application by using the Load Generator which will run with variable of \textbf{25 Users} and \textbf{5 Spawn Rates} for \textbf{1 hour}. This baseline data will then be stored by the engine for use in future test cases. The next step is to carry out experiment testing with cases which will be explained in more detail further.

>>>>

There are two stages that will be carried out to do this experiment test, the first is baseline data collection stage. Baseline data will be taken by simulating
the usage of the application by using the Load Generator which will run with variable of \textbf{25 Users} and \textbf{5 Spawn Rates} for \textbf{1 hour}. This baseline data will then be stored by the engine for use in future test cases. The next step is to carry out experiment testing with cases which will be explained in more detail further.

There are two types of test cases to be tested on the system. Tirst type are cases that simulate regression by making changes that occurs at the application level by making modifications intentionally at the code level.
The first case will have an ID with an SI prefix signifying the \textit{Internal-Scenario}.
The second type are cases that simulate regression by increasing the number of users and load on the Load Generator. The second case will have an ID with the SE prefix denotes an \textit{External-Scenario}. Table IV.5 will explain the cases
system testing.
